Thermal reactionome of a temperate ant species

### 2014-05-15 doc/ApTranscriptome_manuscript.Rmd

We identified 22,399 genes with overall model fits of P < 0.05, retaining 10,597 after correcting for FDR. Of these transcripts, 9,156 significantly change expression with temperature including 6,908 that have a species x temperature interaction. The number of transcripts that increased expression with temperature (*High*), decreased expression with temperature (*Low*), increased expression at both high and low (*Bimodal*) temperatures, decreased expression at high and low temperatures (*Intermediate*) or were not expressed differed significantly between the species ($\chi^2 = 170, P < 0.0001$; Table 1). For both species, the majority of responsive transcripts were in the *Low* category (Fig. 1). More transcripts had *Intermediate* expression in *A. carolinensis* than in *A. picea*, which had nearly twice as many bimodally-expressed transcripts  (Fig. 1, Table 1).

>>>>

We identified `r length(which(RxNpval$pval < 0.05))` genes with overall model fits of *P* < 0.05, retaining `r length(which(RxNpval$padj < 0.05))` after adjusting *P* values for false discovery rate. Of these genes, `r sum(sigtable[sigtable$Coefficient %in% c("Temperature, Temperature:Colony"), "Number.significant"])` significantly change expression with temperature including `r sum(sigtable[sigtable$Coefficient %in% "Temperature:Colony", "Number.significant"])` that have a species x temperature interaction. The number of transcripts that increased expression with temperature (*High*), decreased expression with temperature (*Low*), increased expression at both high and low (*Bimodal*) temperatures, decreased expression at high and low temperatures (*Intermediate*) or were not expressed differed significantly between the species ($\chi^2$ = `r chi1$statistic`, P < `r max(chi1$p.value, 0.0001)`; Table 1). For both species, the majority of responsive transcripts were in the *Low* category (Fig. 1). More transcripts had *Intermediate* expression in *A. carolinensis* than in *A. picea*, which had nearly twice as many bimodally-expressed transcripts  (Fig. 1, Table 1).
